Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-02-28 WSSSPE1_report/WSSSPE1_summary_report.tex
comment

\subsection{Infrastructure software}
%TODO: expand
Infrastructure software is developed to better utilize particular, often new,
infrastructures and architectures, e.g., \emph{MVAPICH}, \emph{VisIT}. Explores
uncharted territories. Highest risk since the projects are experimental.
\note{Dan: so is the only difference here that this category is aimed at new
systems, where utility software is not?  If so, perhaps this should be
incorporated into that subsection, so there would just be two subsections.
Something in the framing of this subsection doesn't feel right to me.
FL: I respectfully disagree the the only reason to develop frameworks is
to better utilize (new or old) infrastructure. Another really important reason
is to modularize development, making it much easier for an individual developer/user
to integrate their own code.}
Successful projects reap high rewards and have longer usage span. By nature,
they overlap with the utility software as they must serve as a facilitator to
run ordinary codes. Long requirement-development-test cycles.  Wide community
support but tends to be handled by specialists rather then end users. Promotes
collaborations across the breadth (e.g., different departments) and depth
(e.g., stakeholders within a department) of community, one of the key
ingredient of a sustainable process. Ferenbaugh~\cite{Ferenbaugh_WSSSPE}
discusses the risks and challenges associated with software projects dealing
with new architectures. To leverage the power of accelerators such as GPUs and
MICs new code and libraries are required. The experience of efforts as
described in~\cite{Ferenbaugh_WSSSPE} met with a limited success but
nonetheless with many invaluable lessons were learned about influential
cultural and technical aspects in sustainable software development practices.

>>>>

\subsection{Infrastructure software}
\todo{expand}
Infrastructure software is developed to better utilize particular, often new,
infrastructures and architectures, e.g., \emph{MVAPICH}, \emph{VisIT}. Explores
uncharted territories. Highest risk since the projects are experimental.
\note{Dan: so is the only difference here that this category is aimed at new
systems, where utility software is not?  If so, perhaps this should be
incorporated into that subsection, so there would just be two subsections.
Something in the framing of this subsection doesn't feel right to me.  FL:
I respectfully disagree the the only reason to develop frameworks is to
better utilize (new or old) infrastructure. Another really important reason
is to modularize development, making it much easier for an individual
developer/user to integrate their own code. Ketan: I think in this section
I wanted to bring up a class of software projects which are undertaken with the
main aim of tackling new systems and architectures in mind. New infrastructures
such as GPU, Cloud, fast IB, federal science networks, etc. were on my mind as I
see many submissions around them in the workshop.}
Successful projects reap
high rewards and have longer usage span. By nature, they overlap with the
utility software as they must serve as a facilitator to run ordinary codes.
Long requirement-development-test cycles.  Wide community support but tends to
be handled by specialists rather then end users. Promotes collaborations across
the breadth (e.g., different departments) and depth (e.g., stakeholders within
a department) of community, one of the key ingredient of a sustainable process.
Ferenbaugh~\cite{Ferenbaugh_WSSSPE} discusses the risks and challenges
associated with software projects dealing with new architectures. To leverage
the power of accelerators such as GPUs and MICs new code and libraries are
required. The experience of efforts as described in~\cite{Ferenbaugh_WSSSPE}
met with a limited success but nonetheless with many invaluable lessons were
learned about influential cultural and technical aspects in sustainable
software development practices.
